Memory-aware Adaptive Scheduling of Scientific Workflows On Heterogeneous Architectures\\

### 2024-10-11 main.tex
related work

\AB{Say why our approach in dynamic setting is different and novel}

@@

Another key contribution is that we have adapted these heuristics for a dynamic setting, where exact
task parameters (execution times and memory requirements) are not know in advance. 
We have implemented a runtime system that interacts with the scheduler, returning exact
parameter values once a task arrives in the system, while only estimates are known for future tasks. 
Some preliminary experiments have been conducted in this setting, and demonstrated that
it is necessary to adapt the schedule on the fly in order to avoid an execution failure because
of a shortage in memory.

>>>>

While several related work consider building a new schedule once some variation has been observed,
we are not aware of work implementing a real runtime system that interacts with the scheduler,
and tested on workflows with thousands of tasks, as we propose in this paper. Furthermore, 
we are not aware of any previous work discussing dynamic algorithms combined with memory constraints. 
%\AB{Say why our approach in dynamic setting is different and novel}

@@

Another key contribution is that we have adapted these heuristics for a dynamic setting, where exact
task parameters (execution times and memory requirements) are not know in advance. 
We have implemented a runtime system that interacts with the scheduler, returning exact
parameter values once a task arrives in the system, while only estimates are known for future tasks. 
Some preliminary experiments have been conducted in this setting, and demonstrated that
it is necessary to adapt the schedule on the fly in order to avoid an execution failure because
of a shortage in memory. To the best of our knowledge, this is the first study of adaptive
algorithms accounting for memory constraints.
